
\documentclass[14pt]{article}
\title{Club Constitution}

\renewcommand{\thesection}{Article \Roman{section}}


\begin{document}

\section{Name of the Organization}
\begin{enumerate}
  \item The name of this organization shall be “Computer Science Club”.
\end{enumerate}

\section{Purpose of the Organization}
\begin{enumerate}
  \item A collection of like-minded computer science students, discussing and taking part in computer science related projects.
\end{enumerate}

\section{Officers of the Organization}
\begin{enumerate}
  \item The elected officers of this club shall be: President, Vice President, Treasurer and Press Secretary.
  \item The term of office shall be one semester.
  \item It shall be the duty of the President to prepare and submit the appropriate paperwork needed for maintaining the club, and to oversee the meetings and elections of the club.
  \item It shall be the duty of the Vice President fulfill the duties of the Presidency in the event that the President is unable to and to assist in any duties as needed by the President.
  \item It shall be the duty of the Treasurer to oversee any financial transactions.
  \item It shall be the duty of the Press Secretary to manage the social media and public relations of the organization.
  \item Elections will be held at the start of every semester to determine the officers of that semester. There shall be a separate election for each position, decided by a simple majority of votes from present members.
  \item Officers can be removed from office with a three fourths vote from all active members with the support of at least one officer and/or the faculty advisor.
\end{enumerate}

\section{Membership}
\begin{enumerate}
  \item All members must be enrolled in at least 1 unit at American River College.
  \item This organization does not and shall not discriminate on the basis of race, color, religion (creed), gender, gender expression, age, national origin (ancestry), disability, marital status, sexual orientation, or military status, in any of its activities or operations.
  \item Members can be removed from the organization by a vote of three fourths active club members with the support of at least one officer and/or the faculty advisor.
  \item Active members are any members that have been present for three club meetings of the current semester and has been or is present for at least one of the three previous or current meeting(s). All persons present for the first six meetings are considered active members during those meetings.
\end{enumerate}

\section{Meetings}
\begin{enumerate}
  \item Meetings occur on Tuesdays and Thursdays, 12:00pm – 3:00pm during the Spring and Fall semesters.
  \item Special meetings may be held at the discretion of the President with at least 24 hours notice.
\end{enumerate}

\section{Quorum}
\begin{enumerate}
  \item Elections may only be held with a majority of active members, including officers present.
\end{enumerate}

\section{Amendments}
\begin{enumerate}
  \item Amendments to this constitution may be proposed by any officer of the club and/or the faculty advisor and approved by a vote of three fourths active club members.
\end{enumerate}

\section{Enacting Clause}
\begin{enumerate}
  \item This constitution shall become effective upon arrival of the Club President, Club Faculty Advisor or Leadership and Development Supervisor.
\end{enumerate}

\end{document}
